---
title: "LogisticRegression_FRA.R"
author: "Prasanta Panja"
date: "3 December 2017"
output: html_document
---

##Importing Libraries

```{r setup, include=FALSE}
# install.packages("caTools")
# install.packages("DMwR")

library("xlsx")
library("car")
library("RColorBrewer")
library("dplyr")
library("DMwR")
library("caTools")
library("ROCR")
```

## Settingup working directory and Reading training data

```{r}
setwd("C:/Users/Prasanta/Downloads/PGPBABI/FRA/GA")
train <- read.xlsx("training.xlsx",sheetName = "training")
```

## Training Data Preparation
## Populating NA's of NumberofDependents 

```{r}
train1 <- train %>% filter(NumberOfDependents != 'NA')
train2 <- train %>% filter(NumberOfDependents == 'NA')

sd(as.numeric(as.character((train1$NumberOfDependents))))
mean(as.numeric(as.character((train1$NumberOfDependents))))
train2$NumberOfDependents <- ceiling(rnorm(142,.74,1.10))
train2$NumberOfDependents <- ifelse(train2$NumberOfDependents < 0,0,train2$NumberOfDependents)
train1$NumberOfDependents <- as.numeric(as.character(train1$NumberOfDependents))
train3 <- rbind(train1,train2)
```
## Scaling of data (RevolvingUtilizationOfUnsecuredLines and DebtRatio)
```{r}
train4 <- train3

train4$NumberOfDependents <- as.numeric(as.character(train4$NumberOfDependents))

train4SD2yrs0 <- train4 %>% filter(SeriousDlqin2yrs == 0)
train4SD2yrs1 <- train4 %>% filter(SeriousDlqin2yrs == 1)

train4SD2yrs0$ScaledRUOfUnsecuredLines <- as.vector(scale(train4SD2yrs0$RevolvingUtilizationOfUnsecuredLines))
train4SD2yrs0$ScaledDebtRatio <- as.vector(scale(train4SD2yrs0$DebtRatio))

train4SD2yrs1$ScaledRUOfUnsecuredLines <- as.vector(scale(train4SD2yrs1$RevolvingUtilizationOfUnsecuredLines))
train4SD2yrs1$ScaledDebtRatio <- as.vector(scale(train4SD2yrs1$DebtRatio))

train5 <- rbind(train4SD2yrs0,train4SD2yrs1)
train5 <- train5[-c(1,3,4)]
```
## Model Building
```{r}
table(train5$SeriousDlqin2yrs)

model <- glm(SeriousDlqin2yrs~., data = train5, family = "binomial")

summary(model)
```

## Test Data Preparation
## Populating NA's of NumberofDependents 

```{r}
test <- read.xlsx("test.xlsx",sheetName = "test")
test1 <- test %>% filter(NumberOfDependents != 'NA')
test2 <- test %>% filter(NumberOfDependents == 'NA')

sd(as.numeric(as.character((test1$NumberOfDependents))))
mean(as.numeric(as.character((test1$NumberOfDependents))))
test2$NumberOfDependents <- ceiling(rnorm(20,.73,1.08))
test2$NumberOfDependents <- ifelse(test2$NumberOfDependents < 0,0,test2$NumberOfDependents)
test1$NumberOfDependents <- as.numeric(as.character(test1$NumberOfDependents))
test3 <- rbind(test1,test2)
```
## Scaling of data (RevolvingUtilizationOfUnsecuredLines and DebtRatio)
```{r}
test4 <- test3

test4$NumberOfDependents <- as.numeric(as.character(test4$NumberOfDependents))

test4SD2yrs0 <- test4 %>% filter(SeriousDlqin2yrs == 0)
test4SD2yrs1 <- test4 %>% filter(SeriousDlqin2yrs == 1)

test4SD2yrs0$ScaledRUOfUnsecuredLines <- as.vector(scale(test4SD2yrs0$RevolvingUtilizationOfUnsecuredLines))
test4SD2yrs0$ScaledDebtRatio <- as.vector(scale(test4SD2yrs0$DebtRatio))

test4SD2yrs1$ScaledRUOfUnsecuredLines <- as.vector(scale(test4SD2yrs1$RevolvingUtilizationOfUnsecuredLines))
test4SD2yrs1$ScaledDebtRatio <- as.vector(scale(test4SD2yrs1$DebtRatio))

test5 <- rbind(test4SD2yrs0,test4SD2yrs1)
test5 <- test5[-c(1,3,4)]
```
## Model validation without SMOTING
```{r}
predictTest <- predict(model, type = "response", newdata = test5)
predictClass <- predictTest > 0.3
confusion_matrix <- table(test5$SeriousDlqin2yrs,predictClass)
confusion_matrix
```
## SMOTING training data
```{r}
train5$SeriousDlqin2yrs <- as.factor(train5$SeriousDlqin2yrs)
train5SMOTED <- SMOTE(SeriousDlqin2yrs~.,train5,perc.over=500,perc.under=300)
table(train5SMOTED$SeriousDlqin2yrs)
traintmp <- train5SMOTED
traintmp$SeriousDlqin2yrs <- as.numeric(as.character(traintmp$SeriousDlqin2yrs))
sum(as.numeric(traintmp$SeriousDlqin2yrs))/nrow(traintmp)
```
## Model validation with SMOTING
```{r}
train5$SeriousDlqin2yrs <- as.numeric(as.character(train5$SeriousDlqin2yrs))
modelSMOTED <- glm(SeriousDlqin2yrs~., data = train5SMOTED, family = "binomial")
summary(modelSMOTED)
predictTestSMOTED <- predict(modelSMOTED, type = "response", newdata = test5)
predictClassSM <- predictTestSMOTED > 0.3
confusion_matrixSM <- table(test5$SeriousDlqin2yrs,predictClassSM)
confusion_matrixSM
```
## ROC curve with SMOTING
```{r}
ROCRpred <- prediction(predictTestSMOTED, test5$SeriousDlqin2yrs)
ROCRperf <- performance(ROCRpred, "tpr", "fpr")
plot(ROCRperf, colorize = TRUE, print.cutoffs.at = seq(0,1,0.1), text.adj = c(-0.2, 1.7))
```
